---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r, include=FALSE}
devtools::load_all(".")
```

# autoLIMR

<!-- badges: start -->
[![R-CMD-check](https://github.com/gemmagerber/autoLIMR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/gemmagerber/autoLIMR/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/gemmagerber/autoLIMR/branch/main/graph/badge.svg)](https://app.codecov.io/gh/gemmagerber/autoLIMR?branch=main)
[![test-coverage](https://github.com/gemmagerber/autoLIMR/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/gemmagerber/autoLIMR/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

The goal of autoLIMR is to automate the construction, calculation, and
evaluation of multiple plausible networks using linear inverse modelling coupled 
with Markov Chain Monte Carlo (LIM-MCMC).

autoLIMR achieves this by:

* Translating network input data into files directly compatible with R packages [LIM](https://cran.r-project.org/web/packages/LIM/index.html) and
[limSolve](https://cran.r-project.org/web/packages/limSolve/index.html)

* Solves multiple plausible networks using LIM-MCMC procedures in
[LIM](https://cran.r-project.org/web/packages/LIM/index.html) and
[limSolve](https://cran.r-project.org/web/packages/limSolve/index.html)

* Evaluates if the multiple plausible networks are representitave of the
original input data using a suite of visual and statistical MCMC diagnostics.

For more information please consult the html vignette (in progress)

## Installation

You can install the latest version of autoLIMR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gemmagerber/autoLIMR")
```


